MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives

### 2017-06-12 ArticleRevision/article/article.tex
Begin port to elsarticle
Reformatting required

%\begin{filecontents*}{MIRSVM.eps}
%gsave
%newpath
%  20 20 moveto
%  20 220 lineto
%  220 220 lineto
%  220 20 lineto
%closepath
%2 setlinewidth
%gsave
%  .4 setgray fill
%grestore
%stroke
%grestore
%\end{filecontents*}
\RequirePackage{fix-cm}
\documentclass[smallcondensed]{svjour3}                 
\smartqed  
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath,amssymb,mathtools,float,times,bm,tikz,proof,tabularx,capt-of,natbib}
\usepackage{graphicx,amsfonts,array,url,algorithm,algorithmicx,algpseudocode,booktabs}
\usepackage[flushleft]{threeparttable}
\usepackage[top=1in,bottom=1in,right=1in,left=1in]{geometry}
\usepackage{tikz-cd,adjustbox}
\usetikzlibrary{shapes.geometric,arrows,automata,positioning}
\usepackage{setspace}
\let\Algorithm\algorithm
\renewcommand\algorithm[1][]{\Algorithm[#1]\setstretch{1}}

@@

\journalname{Machine Learning}

@@

@@

\author{Gabriella Melki \and
        Alberto Cano			\and
        Sebasti\'an Ventura
}

\institute{Gabriella Melki \at
			Virginia Commonwealth University, 401 W. Main St. E2264, Richmond, VA 23284\\
            \email{melkiga@vcu.edu}          
           \and
           Alberto Cano \at
           	Virginia Commonwealth University, 401 W. Main St. E4251, Richmond, VA 23284\\
            \email{acano@vcu.edu}
           \and
           Sebasti\'an Ventura \at
            University of C\'{o}rdoba, ``Albert Einstein Building'', 3rd floor, 14071 C\'{o}rdoba, Spain\\
            \email{sventura@uco.es}
}

@@

\maketitle

\begin{abstract}
\textit{Multiple-instance learning} (MIL) is a variation of \textit{supervised learning}, where samples are represented by labeled bags, each containing sets of instances. The individual labels of the samples within a bag are unknown, and labels are assigned based on a multi-instance assumption. One of the major complexities associated with this type of learning is the ambiguous relationship between a bag's label and the instances it contains. This paper proposes a novel support vector machine (SVM) multiple-instance formulation and presents an algorithm with a bag-representative selector that trains the SVM based on bag-level information, named MIRSVM. The contribution is able to identify instances that highly impact classification, i.e. bag-representatives, for both positive and negative bags, while finding the optimal class separation hyperplane. Unlike other multi-instance SVM methods, this approach eliminates possible class imbalance issues by allowing both positive and negative bags to have at most one representative, while highlighting the instances that contribute most to the classification model. The experimental study evaluates and compares the performance of this proposal against $10$ state-of-the-art multi-instance methods over $15$ datasets, and the results are validated through non-parametric statistical analysis. The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as this proposal's overall superior performance against other multi-instance SVM models. 
\keywords{Machine learning \and multiple-instance learning \and support vector machines \and bag-level multi-instance classification \and bag-representative selection}
\end{abstract}

@@

\begin{acknowledgements}
This research was supported by the Spanish Ministry of Economy and Competitiveness, project TIN2014-55252-P, and by FEDER funds.
\end{acknowledgements}

% BibTeX users please use one of
\bibliographystyle{natbib}
\bibliography{references}

>>>>

\documentclass[preprint,12pt]{elsarticle}
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage[hidelinks]{hyperref}
\usepackage{amsmath,amssymb,mathtools,float,times,bm,tikz,proof,tabularx,capt-of,natbib}
\usepackage{graphicx,amsfonts,array,url,algorithm,algorithmicx,algpseudocode,booktabs}
\usepackage[flushleft]{threeparttable}
\usepackage[top=1in,bottom=1in,right=1in,left=1in]{geometry}
\usepackage{tikz-cd,adjustbox}
\usetikzlibrary{shapes.geometric,arrows,automata,positioning}
\usepackage{setspace}
\let\Algorithm\algorithm
\renewcommand\algorithm[1][]{\Algorithm[#1]\setstretch{1}}

@@

\journal{Pattern Recognition}

@@

\begin{frontmatter}

@@

\author[a]{Gabriella Melki}\author[a]{Alberto Cano}\author[b,c]{Sebasti\'an Ventura}
\address[a]{Department of Computer Science, Virginia Commonwealth University, USA}
\address[b]{Department of Computer Science and Numerical Analysis, University of Cordoba, Spain}
\address[c]{Department of Computer Science, King Abdulaziz University, Saudi Arabia Kingdom}

@@

\begin{abstract}
\textit{Multiple-instance learning} (MIL) is a variation of \textit{supervised learning}, where samples are represented by labeled bags, each containing sets of instances. The individual labels of the samples within a bag are unknown, and labels are assigned based on a multi-instance assumption. One of the major complexities associated with this type of learning is the ambiguous relationship between a bag's label and the instances it contains. This paper proposes a novel support vector machine (SVM) multiple-instance formulation and presents an algorithm with a bag-representative selector that trains the SVM based on bag-level information, named MIRSVM. The contribution is able to identify instances that highly impact classification, i.e. bag-representatives, for both positive and negative bags, while finding the optimal class separation hyperplane. Unlike other multi-instance SVM methods, this approach eliminates possible class imbalance issues by allowing both positive and negative bags to have at most one representative, while highlighting the instances that contribute most to the classification model. The experimental study evaluates and compares the performance of this proposal against $10$ state-of-the-art multi-instance methods over $15$ datasets, and the results are validated through non-parametric statistical analysis. The results indicate that bag-based learners outperform the instance-based and wrapper methods, as well as this proposal's overall superior performance against other multi-instance SVM models. 
\end{abstract}

\begin{keyword}
Machine learning \sep multiple-instance learning \sep support vector machines \sep bag-level multi-instance classification \sep bag-representative selection
\end{keyword}

\end{frontmatter}

@@

\section*{Acknowledgment}
This research was supported by the Spanish Ministry of Economy and Competitiveness, project TIN2014-55252-P, and by FEDER funds.

% BibTeX users please use one of
\bibliographystyle{model1-num-names}
\bibliography{references}
